---
title: "ADAPTS Vignette #5"
subtitle: 'Getting More Consistant Results by Iteratively Building Matrices '
author: "Xinyi Yan"
date: "8/21/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning=FALSE,message=FALSE,dpi = 65,fig.retina = 1.5)
library(devtools) 
devtools::install_github('yxinyi2/ADAPTSdata4')

```

<p>Install ADAPTSdata4 using the code: <p>

<p>install.packages(‘devtools’) <p>

<p>library(devtools) <p>

<p>devtools::install_github(‘yxinyi2/ADAPTSdata4’)<p>


```{r libraries, echo=FALSE, warning=FALSE}
library(ADAPTS)
library(ADAPTSdata4)
library(pheatmap)
library(parallel)
library(ranger)
method <- 'DCQ'
set.seed(42)
doParallel::registerDoParallel(cores = parallel::detectCores())
```


### Construct all the signature matrices one time
<p>This prostate data set comes from Henry, Gervaise H., et al. "A cellular anatomy of the normal adult human prostate and prostatic urethra." Cell reports 25.12 (2018): 3530-3542.<p>
<p>Half of the data are held out as test set by setting 'testOnHalf' to TRUE.<p>
<p>Result tables are for original cell types and clustered cell types relatively.<p>
```{r}
scHenry<-as.matrix(log(ADAPTSdata4::scHenry+1))

resList<-testAllSigMatrices(exprData=scHenry, randomize = TRUE, skipShrink=FALSE, proportional=FALSE,handMetaCluster=NULL,testOnHalf=TRUE)

acc<-cbind(resList$testAcc.shrink,resList$testAcc.aug,resList$testAcc.all,resList$testAcc.seed)
acc<-acc[c(1,3,5,6), ]
acc<-cbind(acc,rep(1,4))
colnames(acc)<-c('Shrunk Matrix','Augmented Matrix','All Gene Matrix','Seed Matrix','actFrac.test')
deconTable<-round(rbind(resList$estimates.onTest,acc),2)

metacc<-cbind(resList$testAcc.metaAugShrink,resList$testAcc.metaAug,resList$testAcc.metaAll,resList$testAcc.metaSeed)
metacc<-metacc[c(1,3,5,6), ]
metacc<-cbind(metacc,rep(1,4))
colnames(metacc)<-c('Shrunk Meta','Augmented Meta','All Gene Meta','Seed Meta','actFrac.test')
metadeconTable<-round(rbind(resList$estimates.onTest.meta,metacc),2)

print(deconTable)
print(metadeconTable)

```





### Construct all the signature matrices iteratively until results converge with 1% tolerance
<p>The iteration stops when Pearson correlation, Spearman's correlation, mae, and rmse all converge.<p>
<p>The result table shows the mean accuracy metrics and at which iteration the corresponding metric converges.<p> 
```{r,fig.show='hide'}
allResListCov<-loopTillConvergence(numLoops=NULL,fastStop=TRUE,exprData=scHenry,changePer=1,handMetaCluster=NULL,testOnHalf=TRUE)
meanResListConv<-meanResults(allResListCov,changePer = 1)
meanResListConvOut<-meanResListConv[c('rho.cor','pVal','spear.rho','mae','rmse','N','convIt.rho.cor','convIt.pVal','convIt.spear.rho','convIt.mae','convIt.rmse')]
print(round(meanResListConvOut,2))
```

### Construct all the signature matrices 20 times with 5% tolerance
The result table shows the mean accuracy metrics of 20 iterations.
```{r,fig.show='hide'}
allResList<-loopTillConvergence(numLoops=20,fastStop=TRUE,exprData=scHenry,changePer=5,handMetaCluster=NULL,testOnHalf=TRUE)
meanResList<-meanResults(allResList,changePer = 5)
meanResListOut<-meanResList[c('rho.cor','pVal','spear.rho','mae','rmse','N','convIt.rho.cor','convIt.pVal','convIt.spear.rho','convIt.mae','convIt.rmse')]
print(round(meanResListOut,2))
```
